### 2012-03-21 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

The next phase marks this occurrence as (O1) case with weight 0.5 and the following statements are inferred:

\begin{itemize}
\item Key $k = (/site/people/person, \{@id\})$ is satisfied.
\item Foreign key $((/site/closed\_auctions/closed\_auction, \{buyer/@person\}) \rightarrow k)$ is satisfied.
\item Key $(/site/closed\_auctions/closed\_auction, \{buyer/@person\})$ is not satisfied.
\end{itemize}

>>>>

\begin{itemize}
\item $P_1 =$ \texttt{/site/people/person}
\item $P_2 =$ \texttt{/site/closed\_auctions/closed\_auction}
\item $L_1 =$ \texttt{@id}
\item $L_2 =$ \texttt{buyer/@person}
\end{itemize}

The next phase marks this occurrence as (O1) case with weight 0.5. Paths $P_1$ and $P_2$ does not have a common context, and thus, the following statements are inferred:

\begin{itemize}
\item Key $k = ($\texttt{/site/people/person}$, \{$\texttt{@id}$\})$ is satisfied.
\item Foreign key $(($\texttt{/site/closed\_auctions/closed\_auction}$, \{$\texttt{buyer/@person}$\}) \rightarrow k)$ is satisfied.
\item Key $($\texttt{/site/closed\_auctions/closed\_auction}$, \{$\texttt{buyer/@person}$\})$ is not satisfied.
\end{itemize}
